Probing the internal structure of quasars using microlensing events

### 2016-03-10 paper1/intro.tex
editing

\section{introduction}
More than half a century after their discovery, quasars still maintain the interest of a productive part of the astrophysical community. 
Although several mechanisms have been proposed to explain how such systems function, a single mechanism is widely accepted at the present time. 
The model was first proposed by \cite{1964ApJ...140..796S}, followed by \cite{1964SPhD....9..246Z} in the same year and \cite{1969Natur.223..690L} five years later.
The present name of the model is the Super-Massive Black Hole (SMBH) paradigm.\\

According to the paradigm, the object is powered through the accretion of matter from the proximal environment into the black hole. 
The radiation emitted excites the surrounding medium which becomes detectable as the narrow line regions, broad band regions and torus. 
Moreover, in the direction perpendicular to the accretion disk, where the medium is more transparent, jets will appear.
When the medium between and observer and such an object is transparent a quasar can be observed \citep[e.g.,][]{1984RvMP...56..255B}. 
In other words an active galactic nucleus (AGN) with one of the poles orientated towards Earth would be detected as a quasar by an observer. \\

Through extensive observations done in the past 50 years, an important part of the set of assumptions and details  regarding the mechanism have been confirmed and uncovered. 
Still, the black hole shadow and the surrounding luminous accreting material (the black hole silhouette) remain to be probed. 
Advancements in the very long baseline interferometer observations have made possible since 2007, the detection of structures of a few Schwarzschild radii of Sgr~A* at the center of our Galaxy \citep{2008JPhCS.131a2055D}. 
Furthermore, jet launching structure near the supermasve black hole in M87 were resolved with the same observation tool \citep{2012Sci...338..355D}.
With all the advancement, the current number of baselines does not allow the direct generation of images from the observations still it does allow the fitting of the data to predefined models \citep{2013MNRAS.434..765K}.

A whole range of models have been applied starting from simple geometric models to more complex, physically sensible models (\cite{2008Natur.455...78D}, \cite{2011ApJ...738...38B}, \cite{2009ApJ...706..497M}, \cite{2010ApJ...717.1092D}, \cite{2016arXiv160205527F}). 
A significant fraction of the later models predict a crescent shaped silhouette of the black hole. 
This motivated \cite{2013MNRAS.434..765K} to use a simple geometric crescent model to fit the data. 
The succesful results encouraged the authors to speculate that the shadow of the black hole will be observed in the near future with the previously mentioned observation method. \\

Hundreds of thousands of quasars have been detected up to date, mainly from the Sloan Digital Sky Survey. The great majority of them present a redshift larger than 2.15 of their spectra (\citep{2014A&A...563A..54P}). 
Therefore the typical distance to the objects is in the order of gigaparsecs or above. 
A value that is orders of magnitude larger than the distance to M87. The direct observations of the black hole silhouettes of quasars require significant technological advances.\\

We argue in the present paper that one can probe and study the black hole shadow and its proximal environment belonging to a quasar without having to resolve sub-event horizon scales. 
We consider that this is possible by analysing the data from microlensing-events as suggested by \cite{1999ApJ...524...49A}. They argue that if the magnification function $\mu_t(p)$ from equation (6) corresponds to a perfect fold then from the function $F(t)$ present in the same equation one can extract the source profile. We argue in the current article that one can partially 
reconstruct the black hole silhouette up to a simplified crescent geometry. The crescent fit facilitates an estimation of the black hole mass.       
Moreover, unlike with the few nearby AGNs, the study of the very large quasar population allows for the statistical refinement of the global properties of AGN by highlighting any particular
characteristic that is present only in Sgr~A* and M87 central region. 
Furthermore, the probing of the event-horizon-scale inner regions of a large number of objects will facilitate the study of the evolution of the previously mentioned region. \\

>>>>

\section{introduction}

Active galactic nucleii are thought to be powered through the
accretion of matter from the proximal environment into a supermassive
black hole.  The radiation emitted excites the surrounding medium
which becomes detectable as narrow line regions, broad line regions
and optical continuum.  Moreover, in the direction perpendicular to
the accretion disk, where the medium is more transparent, jets will
appear.  If a jet is oriented towards the Earth, a quasar is observed
\citep[e.g.,][]{1984RvMP...56..255B}.  While the basic mechanism
\citep[originating in the work
  of][]{1964ApJ...140..796S,1964SPhD....9..246Z,1969Natur.223..690L}
is not in doubt, the central engines, near the event horizons of the
black holes, remain to be probed.

For the black holes in the Galactic centre and the centre of M87
---the two nearest objects that barely qualify as AGN--- the central
engines (which are $<0.1\rm\,mas$ on the sky) are close to being
resolved through very long baseline interferometry, which shows
preliminary indications of the jet-launching structures
\citep{2008JPhCS.131a2055D,2012Sci...338..355D,2013MNRAS.434..765K,2016arXiv160205527F}.
Current data do not deliver images, but require fitting to to
predefined models for the images.  A whole range of models have been
applied, starting from simple geometric models to more complex
physical models
\citep{2008Natur.455...78D,2011ApJ...738...38B,2009ApJ...706..497M,2010ApJ...717.1092D}.
The more complicated models nonetheless tend to predict a crescent
shaped silhouette of the black hole.  This motivated
\cite{2013MNRAS.434..765K} to use a simple geometric crescent model to
fit the data, and argued that the crescent is nothing but the
silhouette of the event horizon.

The great majority of quasars, however, lie at redshifts beyond 2
\citep{2014A&A...563A..54P} and their central engines would be orders
of magnitude smaller on the sky. The direct observations of the black
hole silhouettes of quasars is far beyond foreseeable instrumentation.
In the present paper we consider a possible indirect method,
previously investigated by \cite{1999ApJ...524...49A}, through which
caustics in gravitational microlensing could probe the black hole
shadow and its proximal quasar environment.

They argue that if the magnification function $\mu_t(p)$ from equation (6) corresponds to a perfect fold then from the function $F(t)$ present in the same equation one can extract the source profile. We argue in the current article that one can partially 
reconstruct the black hole silhouette up to a simplified crescent geometry. The crescent fit facilitates an estimation of the black hole mass.       
Moreover, unlike with the few nearby AGNs, the study of the very large quasar population allows for the statistical refinement of the global properties of AGN by highlighting any particular
characteristic that is present only in Sgr~A* and M87 central region. 
Furthermore, the probing of the event-horizon-scale inner regions of a large number of objects will facilitate the study of the evolution of the previously mentioned region. \\
